A White Noise Approach to Evolutionary Ecology

### 2020-04-02 .A White Noise Approach To Evolutionary Ecology/draft.Rmd
fig4Updated!

\begin{multline}\label{N_det}
\frac{d}{dt}N(t)=\frac{d}{dt}\int_{-\infty}^{+\infty}\nu(x,t)dx=\int_{-\infty}^{+\infty}\frac{\partial}{\partial t}\nu(x,t)dx \\
=\int_{-\infty}^{+\infty} m(\nu,x)\nu(x,t)dx+\int_{-\infty}^{+\infty}\frac{\mu}{2}\frac{\partial^2}{\partial x^2}\nu(x,t)dx \\
=N(t)\int_{-\infty}^{+\infty} m(\nu,x)p(x,t)dx=\bar m(t) N(t).
\end{multline}
Using our assumptions on mutation and rate of growth, we show in SM \S\ref{} $\nu(x,t)$ is twice differentiable with respect to $x$ and $\int_{-\infty}^{+\infty}\nu(x,t)dx<\infty$ for all $t\geq0$. This implies that we are justified in swapping the order of differentiation and integration and the result $\int_{-\infty}^{+\infty}\frac{\partial^2}{\partial x^2}\nu(x,t)dx=0$ can be derived from the fundamental theorem of calculus. Biological reasoning agrees with this latter result since mutation neither creates nor destroys individuals, but merely changes their type from their parental type. Taking the same approach, we derive the dynamics of the phenotypic distribution $p(x,t)$ in response to selection and muation as

@@

```{r, echo=F, fig.align='center', fig.cap='\\label{net}Networks of interspecific interactions parameterized by competition coffecients (top row) and distributions of pairwise coevolution (bottom row) under the scenarios of weak competition (left) and strong competition (right) at time $t=1.0\\times 10^3$ Node sizes are proportional to population sizes. Edge widths and shade are monotonically increasing functions of pairwise coevolution.'}
knitr::include_graphics('on_pl.png')
```

@@

__The genetic architecture and distributions of traits and the role of sexual reproduction__

@@

__The role of ecological stoichiometry__

@@

where $\delta(x-\xi_i(t))$ denotes the point mass located at $\xi_i(t)$. To allow for imperfect heritability, we also track the set of breeding values which, at time $t$, is denoted by $\{\gamma_1(t),\dots,\gamma_{N(t)}(t)\}$ and should not be confused with the quadratic selection gradients discussed in \S\ref{} of the main text. Then the distribution of breeding values can be written as

@@

The imposes the restriction $V>\mathscr{W}(\nu,\xi_i)$. For each offpsring produced by the individual with breeding value $\gamma_i(t)$, we assign indepently drawn breeding values normally distributed around $\gamma_i(t)$ with variance $\mu$. After breeding values have been assigned, we randomly draw trait values for each offpsring as described above. For an overview of our model of inheritance, see \S\ref{} of the main text. This summarizes the basic structure of our simulation. To impose selection and density dependent growth rates, we set

@@

\begin{multline}
d\sigma^2=d\overline{x^2}-2\bar xd\bar x-(d\bar x)^2
=\left(\mathrm{Cov}_t\Big(x^2,m\Big) + \mu \right)dt+\frac{\|\tilde{\tilde\sigma}^2\|_2}{N}d\tilde W_3-\overline{x^2}\sqrt\frac{V}{N}d W_1 \\ \\
-2\bar x\left(\mathrm{Cov}_t(x,m)+\mu dt+\sqrt{\frac{V\sigma^2}{N}}d W_2\right)-\left(\mathrm{Cov}_t(x,m)dt+\mu dt+\sqrt{\frac{V\sigma^2}{N}}d W_2\right)^2 \\ \\
=\left(\mathrm{Cov}_t\Big(x^2-2\bar xx,m\Big) + \frac{\mu}{2}\int_\mathbb{R}(x^2-x\bar x)\Delta p(x,t)dx \right)dt+\frac{\|\tilde{\tilde\sigma}^2\|_2}{N}d\tilde W_3-\overline{x^2}\sqrt\frac{V}{N}d W_1-2\bar x\sqrt{\frac{V\sigma^2}{N}}d W_2-\left(\frac{V\sigma^2}{N}\right)dt \\ \\
=\left(\mathrm{Cov}_t\Big(x-\bar x)^2,m\Big) + \frac{\mu}{2}\int_\mathbb{R}(x-\bar x)^2\Delta p(x,t)dx - \frac{V\sigma^2}{N}\right)dt+\frac{\|\tilde{\tilde\sigma}^2\|_2}{N}d\tilde W_3-\overline{x^2}\sqrt\frac{V}{N}d W_1-2\bar x\sqrt{\frac{V\sigma^2}{N}}d W_2.
\end{multline}

>>>>

\begin{multline}\label{N_det}
\frac{d}{dt}N(t)=\frac{d}{dt}\int_{-\infty}^{+\infty}\nu(x,t)dx=\int_{-\infty}^{+\infty}\frac{\partial}{\partial t}\nu(x,t)dx \\
=\int_{-\infty}^{+\infty} m(\nu,x)\nu(x,t)dx+\int_{-\infty}^{+\infty}\frac{\mu}{2}\frac{\partial^2}{\partial x^2}\nu(x,t)dx \\
=N(t)\int_{-\infty}^{+\infty} m(\nu,x)p(x,t)dx=\bar m(t) N(t).
\end{multline}
Using our assumptions on mutation and rate of growth, we show in SM \S\ref{finite} $\nu(x,t)$ is twice differentiable with respect to $x$ and $\int_{-\infty}^{+\infty}\nu(x,t)dx<\infty$ for all $t\geq0$. This implies that we are justified in swapping the order of differentiation and integration and the result $\int_{-\infty}^{+\infty}\frac{\partial^2}{\partial x^2}\nu(x,t)dx=0$ can be derived from the fundamental theorem of calculus. Biological reasoning agrees with this latter result since mutation neither creates nor destroys individuals, but merely changes their type from their parental type. Taking the same approach, we derive the dynamics of the phenotypic distribution $p(x,t)$ in response to selection and muation as

@@

smpl_wc1e3 = read.csv("/home/bb/Gits/branching.brownian.motion.and.spde/sample_path_wc1e3.csv")

x = smpl_wc1e3$x
G = smpl_wc1e3$G
N = smpl_wc1e3$N

w = 0.1
c = 1e-8
eta = 1.0
R = 1.0
a = 1e-2
th = 0
S = length(x)

Cadf_WC = data.frame(Coev=Cvec,Comp=avec, Which="WC")

smpl_mc1e3 = read.csv("/home/bb/Gits/branching.brownian.motion.and.spde/sample_path_mc1e3.csv")

x = smpl_mc1e3$x
G = smpl_mc1e3$G
N = smpl_mc1e3$N

w = 0.1
c = 5e-7
eta = 1.0
R = 1.0
a = 1e-2
th = 0
S = length(x)

Cadf_SC = data.frame(Coev=Cvec,Comp=avec, Which="SC")

# bivariate plot
Cadf = rbind(Cadf_WC,Cadf_SC)

on_pl = ggplot(Cadf_SC, aes(Coev,Comp)) + 
  scale_x_log10(limits=c(1e-5,2e-4)) + 
  geom_density_2d(col="black",n=200) +
  geom_density_2d(data=Cadf_WC, linetype="dashed", col="black") +
  theme_minimal() + xlab("Pairwise Coevolution") + ylab("")

on_pl2 = on_pl + facet_grid(rows=vars(Which), scales="free_y") + 
  ylab("Competition Coefficient") + theme(strip.background = element_blank(), strip.text.y = element_blank())

ggsave("~/Gits/branching.brownian.motion.and.spde/.A White Noise Approach To Evolutionary Ecology/on_pl.png",on_pl2,device="png",width=3.5,height=3.5,units="in")
```

```{r, echo=F, fig.align='center', fig.cap='\\label{net}Bivariate distributions of competition coffecients (y-axis) and pairwise coevolution (x-axis) under the scenarios of weak competition (dashed line) and strong competition (solid line) after simulating for $t=1000.0$ units of time. Simulations were ran for $S=1000$ species. Parameters are the same as in Table 2, except we used $c=1\\times 10^{-8}$ for weak competition and $c=5\\times 10^{-7}$ for strong competition in order to account for increased species richness.'}
knitr::include_graphics('on_pl.png')
```

@@

__The genetic architecture and distributions of traits__

@@

__Ecological stoichiometry__

@@

where $\delta(x-\xi_i(t))$ denotes the point mass located at $\xi_i(t)$. To allow for imperfect heritability, we also track the set of breeding values which, at time $t$, is denoted by $\{\gamma_1(t),\dots,\gamma_{N(t)}(t)\}$ and should not be confused with the quadratic selection gradients discussed in \S\ref{diffuse} of the main text. Then the distribution of breeding values can be written as

@@

The imposes the restriction $V>\mathscr{W}(\nu,\xi_i)$. For each offpsring produced by the individual with breeding value $\gamma_i(t)$, we assign indepently drawn breeding values normally distributed around $\gamma_i(t)$ with variance $\mu$. After breeding values have been assigned, we randomly draw trait values for each offpsring as described above. For an overview of our model of inheritance, see \S\ref{inheritance} of the main text. This summarizes the basic structure of our simulation. To impose selection and density dependent growth rates, we set

@@

\begin{multline}
d\sigma^2=d\overline{x^2}-2\bar xd\bar x-(d\bar x)^2
=\left(\mathrm{Cov}_t\Big(x^2,m\Big) + \mu \right)dt+\frac{\|\tilde{\tilde\sigma}^2\|_2}{N}d\tilde W_3-\overline{x^2}\sqrt\frac{V}{N}d W_1 \\ \\
-2\bar x\left(\mathrm{Cov}_t(x,m)+\mu dt+\sqrt{\frac{V\sigma^2}{N}}d W_2\right)-\left(\mathrm{Cov}_t(x,m)dt+\mu dt+\sqrt{\frac{V\sigma^2}{N}}d W_2\right)^2 \\ \\
=\left(\mathrm{Cov}_t\Big(x^2-2\bar xx,m\Big) + \mu \right)dt+\frac{\|\tilde{\tilde\sigma}^2\|_2}{N}d\tilde W_3-\overline{x^2}\sqrt\frac{V}{N}d W_1-2\bar x\sqrt{\frac{V\sigma^2}{N}}d W_2-\left(\frac{V\sigma^2}{N}\right)dt \\ \\
=\left(\mathrm{Cov}_t\Big(x-\bar x)^2,m\Big) + \mu - \frac{V\sigma^2}{N}\right)dt+\frac{\|\tilde{\tilde\sigma}^2\|_2}{N}d\tilde W_3-\overline{x^2}\sqrt\frac{V}{N}d W_1-2\bar x\sqrt{\frac{V\sigma^2}{N}}d W_2.
\end{multline}
